---
title: "Ryan Tillis - Exploratory Data Analysis- Data Science - Quiz 1 - Coursera"
author: <a href="http://www.ryantillis.com"> Ryan Tillis </a>
date: "July 6, 2016"
output: github_document
---

## Exploratory Data Analysis Quiz 1

This is Quiz 1 from the Exploratory Data Analysis course

###Questions
<hr>
<font size="+2">1.  </font> Which of the following is a principle of analytic graphics?

<hr>

<font size="+1">
<b>

* Show causality, mechanism, explanation

</b>
</font>

<hr>

```{r Question 1}

```

<hr>

<font size="+2">2.  </font> What is the role of exploratory graphs in data analysis?

<hr>

<font size="+1">
<b>

* They are typically made very quickly.

</b>
</font>

<hr>

```{r Question 3}
library(jpeg)

download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg", destfile = "quiz2jpeg.jpg")
jpgdat = readJPEG("quiz2jpeg.jpg", native = TRUE)
quantile(jpgdat, probs = c(0.3, 0.8))
```

<hr>

<font size="+2">3.  </font> Which of the following is true about the base plotting system?

<hr>

<font size="+1">
<b>

* Plots are created and annotated with separate functions

</b>
</font>

<hr>
```{r Question 4}

```

<hr>

<font size="+2">4.  </font> Which of the following is an example of a valid graphics device in R?

<hr>

<font size="+1">
<b>

* A PDF file

</b>
</font>

<hr>

```{r Question 5}

```

<hr>

<font size="+2">5.  </font> Which of the following is an example of a vector graphics device in R?

<hr>

<font size="+1">
<b>

* SVG

</b>
</font>

<hr>

```{r Question 6}

```

<hr>

<font size="+2">6.  </font> Bitmapped file formats can be most useful for

<hr>

<font size="+1">
<b>

* Scatterplots with many many points

</b>
</font>

<hr>

```{r Question 7}

```

<hr>

<font size="+2">7.  </font> Which of the following functions is typically used to add elements to a plot in the base graphics system?

<hr>

<font size="+1">
<b>

* text()

</b>
</font>

<hr>

<font size="+2">8.  </font> Which function opens the screen graphics device for the Mac?

<hr>

<font size="+1">
<b>

* quartz()

</b>
</font>

<hr>

<font size="+2">9.  </font> What does the 'pch' option to par() control?

<hr>

<font size="+1">
<b>

* the plotting symbol/character in the base graphics system

</b>
</font>

<hr>

<font size="+2">10.  </font> 
If I want to save a plot to a PDF file, which of the following is a correct way of doing that?

<hr>

<font size="+1">
<b>

* Construct the plot on the screen device and then copy it to a PDF file with dev.copy2pdf()

</b>
</font>

<hr>

See more at: <http://www.ryantillis.com/>

<hr>
